# Chapter 2: Regression Analysis

### About the data
  In this exercise we are going to analyze student's attitude towards statistics, based on the survey conducted in 2014. The initial survey was conducted in Finnish and was measured on the [Likert Scale][1](1-5).
  
  For the analysis, we convert the original data to a tabular format where each column represents questions and rows contain individual response from the participants.
  The items of the central measure are named so that the connections to the corresponding dimensions (Deep/SUrface/STrategic) can be easily seen.
  The analysis will be carried across 7 variables: "age", "gender", "attitude", "deep", "strategic", "surface" and "points" distributed in 7 columns and on 166 student observations.
  
  More information on data can be found [here][2].
  
  [1]:https://en.wikipedia.org/wiki/Likert_scale
  [2]:https://www.mv.helsinki.fi/home/kvehkala/JYTmooc/JYTOPKYS3-meta.txt

```{r}
date()
```

##### *Before we beging (setup):*

```{r}
# Setting up working directory of R session into IODS project folder
setwd("~/Workspace/r-studio-projects/IODS-project")

#read data into memory
students2014 <- read.table("./Data/learning2020.table", header=TRUE)

#Structure of the data
str(students2014)

#Dimension of the data
dim(students2014)

library(GGally)
library(ggplot2)

```


#### **Overview of data (in graph form)**

```{r}

p <- ggpairs(students2014, mapping = aes(), lower = list(combo = wrap("facethist", bins = 20)))
p

```


#### **Regression analysis across *age - deep - exam points* **

```{r}

g1 <- ggplot(students2014, aes(x = deep, y = Points, col = Age))
g2 <- g1 + geom_point()
g3 <- g2 + geom_smooth(method = "lm")
g3

```


#### **Diagnostic report - Residual vs Fitted values, Normal QQ-plot and Residuals vs Leverage**

```{r}

my_model <- lm(Points ~ Age + deep, data = students2014)

summary(my_model)


```